Blocking-resistant communication\\through domain fronting

### 2014-08-01 docs/meek.tex
Typos
Change some "meek" into "\meek"

Domain fronting and HTTPS take care of two big circumvention challenges,
those of hiding the destination and of obscuring the contents of a message.
There remain other, more subtle, attributes of communication
that could serve as a basis for blocking.
For example, the plaintext handshake is a fingerprintable part of TLS.
Section~\ref{sec:browserextension} describes how we use a web browser extension as an instrument for making HTTPS requests,
to make \meek's TLS and HTTPS characteristics
match those of a browser as closely as possible.
One of our goals is to force the censor
to employ more sophisticated, expensive, and error-prone statistical tests
to classify traffic as allowed or prohibited,
rather than simple domain blacklists or deep packet inspection;
to force the practice of censorship to exist in a world
not of simple packet filters,
but of probabilities and false positives.
A preliminary analysis of \meek's resistance to detection
based on traffic characteristics like packet length distribution
appears in Section~\ref{sec:trafficanalysis}.
The analysis is based on comparing traffic traces of meek
with samples of HTTPS traffic at an Internet router.

@@

This section contains a brief survey of fronting-capable
web services we have found, each with its pros and cons.
The list is not exhaustive and is meant to illustrate the broad
support for fronting that exists.
Of the services listed, we have so far deployed meek
only on Google App Engine and Amazon CloudFront.
For the others, we have only checked that fronting works.
Recall that even web services that support fronting
will front only for their own customers,
so new each deployment typically means becoming a customer and an investment of time and money.

@@

\begin{figure}
\centering
\includegraphics[width=\linewidth]{flowduration}
\caption{
CDF of connection lifetime.
The horizontal axis is logarithmic.
meek's connections tend to last longer than those of ordinary HTTPS traffic.
}
\label{fig:duration}
\end{figure}

@@

In light of these findings,
the censor may decide to block any long-lived HTTPS connections between
a client and a web service.
According to our traffic trace, doing so will not disrupt more than 8\% of ordinary connections;
whether that is an acceptable cost depends on the censor's
tolerance for collateral damage.
The censor can lower the timing threshold, at the cost of more false positives.
Duration-based blocking is favorable for the circumventor,
because if the censor terminates connections after, say, 10 minutes,
in any case that's 10 minutes of circumvention achieved,
after which \meek can start a new connection
and allow Tor to rebuild its circuits.
Future enhancements in meek may even allow reconnecting using the same session ID,
so there will be no effect on the client other than a brief delay
while a new HTTPS connection is established.

@@

\begin{figure}
\centering
\includegraphics[width=\linewidth]{concurrent.pdf}
\caption{
Number of simultaneous HTTPS connections to any Google server.
Each pale line indicates the number of HTTPS connections
of a single client IP address.
The LBL trace shows 2,745 unique clients and the meek trace only one.
The dark line is a smoothed average number of connections per client.
The meek count stays close to~1 throughout, only momentarily
jumping to 0 or~2.
The average number of connections per user in the LBL trace is 2.61,
and in the meek trace is 1.002.
}
\label{fig:concurrent}
\end{figure}

The number of concurrent connections is another potential distinguisher.
We have seen how meek tends to use one long-lived connection
through which it tunnels all its requests.
Figure~\ref{fig:concurrent} compares the number of concurrent HTTPS connections to
Google per client in both traces.
The number of connections in the LBL trace is variable,
with some hosts briefly spiking up above 50 connections,
but the average case is very heavily skewed to smaller numbers.
The average number of connections in the LBL trace is 2.61,
while in the meek trace it is almost exactly 1, only briefly
deviating when one connection ends and another begins.
We conclude that having a small number of concurrent connections is unremarkable.

% TODO: Since the average numbers of connections are quite different, reviewers may think
% it is remarkable. We should probably show a large percentage of users in the LBL trace only
% have 1~2 connections throughout. Therefore a meek user is a needle in the haystack.

@@

So far we do not find any obvious traffic characteristics that can be useful to reliably distinguish meek
from other HTTPS traffic.
The long-lived connections and few common packet sizes are
potential targets for a more concerted attack.
The fundamental problem we face is essentially that of steganography,
the need to make our traffic fit some model of ``normal'' traffic.
The problem is inherently difficult,
because it is difficult to say just what normal traffic \emph{is}.
It depends on the network environment;
it also depends on the endpoint.
Google's traffic is different than Akamai's.

@@

Development on meek as a Tor pluggable transport~\cite{pt} began in January~2014.
Most users who use Tor, use it with Tor Browser~\cite{torbrowser},
a customized version of Firefox that is
preconfigured to use a built-in Tor client.
% and patched to defend against application-layer privacy and anonymity threats
% like tracking cookies and web browser fingerprinting.
Tor Browser has an easy interface for selecting pluggable transports.
We made a series experimental releases of Tor Browser featuring meek,
releasing the first one on February~18.
On April~18 we made the first release featuring the browser camouflage
that is the subject of Section~\ref{sec:browserextension}.
We announced our releases on Tor development mailing lists,
whence they were picked up by Tor Weekly News on the Tor blog.
Our code was merged by the Tor Browser maintainers
in June and is scheduled for an alpha release,
still pending as of this writing.

@@

\begin{figure}
\includegraphics[width=\linewidth]{clients-psiphon3}
\caption{
Daily unique users of \meek with Psiphon (note vertical axis).
The decrease at the end of June
was caused by an unblocking event that made meek unnecessary for some users.
}
\label{fig:clients-psiphon3}
\end{figure}

@@

Psiphon began their deployment of meek in June~2014.
Figure~\ref{fig:clients-psiphon3} shows the number
of unique daily users of meek with Psiphon,
estimated through clients' self-reporting of their most recent connection date.
The Psiphon developers tell us that the drop that occurs
in the middle of June was not caused by a blocking event,
but rather an unblocking event that made meek unnecessary for some users.
Although Figures~\ref{fig:clients-tor} and~\ref{fig:clients-psiphon3}
are not directly comparable because they count slightly different things,
it is clear that meek-with-Psiphon, with its thousands of daily users,
is much more widely used than meek-with-Tor, which has not yet seen a formal release,

@@

A longer-term goal is to find a way to fund continued operation
if meek becomes popular.
Although some of the systems listed in Section~\ref{sec:survey}
are inexpensive enough that some users could upload their own fronting backend,
thereby diffusing costs,
we believe that an organization operating a backend for the use of the public
has compelling usability advantages.
With client software configured to use the public backend by default,
there is nothing for the user to upload and no out-of-band communication is needed before getting
started---when everything works it offers no-configure circumvention.

@@

The current implementation of meek strictly serializes
its HTTPS requests and responses,
in order to keep chunks of the underlying TCP stream
in the proper order.
The unfortunate side effect of this simple approach
is added latency that gets worse with longer round-trip times.
In future work we plan to add an additional reliability layer,
perhaps like the system of sequence numbers and acknowledgments used in OSS~\cite{oss},
that would allow requests to be pipelined
and cope with out-of-order delivery.
Figure~\ref{fig:wire-sequential} shows how the current implementation works,
and Figure~\ref{fig:wire-parallel} shows the nature of the performance
improvement that could be gained with a reliability layer
and parallel requests.
% Would be useful for Iran-like session cutoff, independent of \meek.

meek's use of HTTPS is subject to the usual public key infrastructure
and trust model.
The browser running the HTTPS camouflage extension (Section~\ref{sec:browserextension})
has a list of trusted certificate authorities.
A censor that controls a certificate authority trusted by the browser
would be able to do a man-in-the-middle attack
between the client and the intermediate web service,
and detect fronting by decrypting TLS and checking for specific Host headers.
Such a censor would be able to detect circumvention,
but still not read the client's plaintext because of the
additional encryption and authentication of the tunneled Tor layer.
It seems risky for the censor to risk being detected in
a man-in-the-middle attack merely to confirm that a user is circumventing,
but it is not impossible for a sufficiently powerful censor.
The problem doesn't exist when the front domain is one
that happens have its public key ``pinned'' in the headless browser,
for instance when using the Chrome extension and fronting through
\urll{www.google.com}.

@@

The key idea of meek is domain fronting,
but its HTTP tunneling ability is useful on its own.
Another idea for deployment is to use
thousands of simple HTTP reflectors on cheap web hosting
(in place of domain fronting on a big CDN).
The request-reflecting role of a CDN can
be played by a PHP script, for example,
or a special web server configuration.
Their URLs unprotected by domain fronting,
each reflector would be easily individually blockable,
so there would need to be sufficiently many that
a censor could not block them all.
This deployment model is essentially the same as with
ordinary Tor bridges: have lots of volunteer-operated bridges
and make it hard to enumerate them all.
The advantage that an HTTP transport would have
is that it is easier for a volunteer to upload a PHP file to a web host
than to set up and maintain a Tor bridge.

@@

We have presented domain fronting,
an HTTPS technique that uses different domain names
at different communication layers in
order to hide the remote endpoint of a communication.
We implemented meek,
a pluggable transport for Tor.
We show that it resists common methods of blocking,
and begin an investigation into its
resistance against more subtle and expensive means of traffic analysis.
We discuss the results of an initial deployment of meek
in both Tor and Psiphon.

>>>>

Domain fronting and HTTPS take care of two big circumvention challenges,
those of hiding the destination and of obscuring the contents of a message.
There remain other, more subtle, attributes of communication
that could serve as a basis for blocking.
For example, the plaintext handshake is a fingerprintable part of TLS.
Section~\ref{sec:browserextension} describes how we use a web browser extension as an instrument for making HTTPS requests,
to make \meek's TLS and HTTPS characteristics
match those of a browser as closely as possible.
One of our goals is to force the censor
to employ more sophisticated, expensive, and error-prone statistical tests
to classify traffic as allowed or prohibited,
rather than simple domain blacklists or deep packet inspection;
to force the practice of censorship to exist in a world
not of simple packet filters,
but of probabilities and false positives.
A preliminary analysis of \meek's resistance to detection
based on traffic characteristics like packet length distribution
appears in Section~\ref{sec:trafficanalysis}.
The analysis is based on comparing traffic traces of \meek
with samples of HTTPS traffic at an Internet router.

@@

This section contains a brief survey of fronting-capable
web services we have found, each with its pros and cons.
The list is not exhaustive and is meant to illustrate the broad
support for fronting that exists.
Of the services listed, we have so far deployed \meek
only on Google App Engine and Amazon CloudFront.
For the others, we have only checked that fronting works.
Recall that even web services that support fronting
will front only for their own customers,
so new each deployment typically means becoming a customer and an investment of time and money.

@@

\begin{figure}
\centering
\includegraphics[width=\linewidth]{flowduration}
\caption{
CDF of connection lifetime.
The horizontal axis is logarithmic.
\meek's connections tend to last longer than those of ordinary HTTPS traffic.
}
\label{fig:duration}
\end{figure}

@@

In light of these findings,
the censor may decide to block any long-lived HTTPS connections between
a client and a web service.
According to our traffic trace, doing so will not disrupt more than 8\% of ordinary connections;
whether that is an acceptable cost depends on the censor's
tolerance for collateral damage.
The censor can lower the timing threshold, at the cost of more false positives.
Duration-based blocking is favorable for the circumventor,
because if the censor terminates connections after, say, 10 minutes,
in any case that's 10 minutes of circumvention achieved,
after which \meek can start a new connection
and allow Tor to rebuild its circuits.
Future enhancements in \meek may even allow reconnecting using the same session ID,
so there will be no effect on the client other than a brief delay
while a new HTTPS connection is established.

@@

\begin{figure}
\centering
\includegraphics[width=\linewidth]{concurrent.pdf}
\caption{
Number of simultaneous HTTPS connections to any Google server.
Each pale line indicates the number of HTTPS connections
of a single client IP address.
The LBL trace shows 2,745 unique clients and the \meek trace only one.
The dark line is a smoothed average number of connections per client.
The \meek count stays close to~1 throughout, only momentarily
jumping to 0 or~2.
The average number of connections per user in the LBL trace is 2.61,
and in the \meek trace is 1.002.
}
\label{fig:concurrent}
\end{figure}

The number of concurrent connections is another potential distinguisher.
We have seen how \meek tends to use one long-lived connection
through which it tunnels all its requests.
Figure~\ref{fig:concurrent} compares the number of concurrent HTTPS connections to
Google per client in both traces.
The number of connections in the LBL trace is variable,
with some hosts briefly spiking up above 50 connections,
but the average case is very heavily skewed to smaller numbers.
The average number of connections in the LBL trace is 2.61,
while in the \meek trace it is almost exactly 1, only briefly
deviating when one connection ends and another begins.
We conclude that having a small number of concurrent connections is unremarkable.

% TODO: Since the average numbers of connections are quite different, reviewers may think
% it is remarkable. We should probably show a large percentage of users in the LBL trace only
% have 1~2 connections throughout. Therefore a \meek user is a needle in the haystack.

@@

So far we do not find any obvious traffic characteristics that can be useful to reliably distinguish \meek
from other HTTPS traffic.
The long-lived connections and few common packet sizes are
potential targets for a more concerted attack.
The fundamental problem we face is essentially that of steganography,
the need to make our traffic fit some model of ``normal'' traffic.
The problem is inherently difficult,
because it is difficult to say just what normal traffic \emph{is}.
It depends on the network environment;
it also depends on the endpoint.
Google's traffic is different than Akamai's.

@@

Development on \meek as a Tor pluggable transport~\cite{pt} began in January~2014.
Most users who use Tor, use it with Tor Browser~\cite{torbrowser},
a customized version of Firefox that is
preconfigured to use a built-in Tor client.
% and patched to defend against application-layer privacy and anonymity threats
% like tracking cookies and web browser fingerprinting.
Tor Browser has an easy interface for selecting pluggable transports.
We made a series experimental releases of Tor Browser featuring \meek,
releasing the first one on February~18.
On April~18 we made the first release featuring the browser camouflage
that is the subject of Section~\ref{sec:browserextension}.
We announced our releases on Tor development mailing lists,
whence they were picked up by Tor Weekly News on the Tor blog.
Our code was merged by the Tor Browser maintainers
in June and is scheduled for an alpha release,
still pending as of this writing.

@@

\begin{figure}
\includegraphics[width=\linewidth]{clients-psiphon3}
\caption{
Daily unique users of \meek with Psiphon (note vertical axis).
The decrease at the end of June
was caused by an unblocking event that made \meek unnecessary for some users.
}
\label{fig:clients-psiphon3}
\end{figure}

@@

Psiphon began their deployment of \meek in June~2014.
Figure~\ref{fig:clients-psiphon3} shows the number
of unique daily users of \meek with Psiphon,
estimated through clients' self-reporting of their most recent connection date.
The Psiphon developers tell us that the drop that occurs
in the middle of June was not caused by a blocking event,
but rather an unblocking event that made \meek unnecessary for some users.
Although Figures~\ref{fig:clients-tor} and~\ref{fig:clients-psiphon3}
are not directly comparable because they count slightly different things,
it is clear that meek-with-Psiphon, with its thousands of daily users,
is much more widely used than meek-with-Tor, which has not yet seen a formal release,

@@

A longer-term goal is to find a way to fund continued operation
if \meek becomes popular.
Although some of the systems listed in Section~\ref{sec:survey}
are inexpensive enough that some users could upload their own fronting backend,
thereby diffusing costs,
we believe that an organization operating a backend for the use of the public
has compelling usability advantages.
With client software configured to use the public backend by default,
there is nothing for the user to upload and no out-of-band communication is needed before getting
started---when everything works it offers no-configure circumvention.

@@

The current implementation of \meek strictly serializes
its HTTPS requests and responses,
in order to keep chunks of the underlying TCP stream
in the proper order.
The unfortunate side effect of this simple approach
is added latency that gets worse with longer round-trip times.
In future work we plan to add an additional reliability layer,
perhaps like the system of sequence numbers and acknowledgments used in OSS~\cite{oss},
that would allow requests to be pipelined
and cope with out-of-order delivery.
Figure~\ref{fig:wire-sequential} shows how the current implementation works,
and Figure~\ref{fig:wire-parallel} shows the nature of the performance
improvement that could be gained with a reliability layer
and parallel requests.
% Would be useful for Iran-like session cutoff, independent of \meek.

\meek's use of HTTPS is subject to the usual public key infrastructure
and trust model.
The browser running the HTTPS camouflage extension (Section~\ref{sec:browserextension})
has a list of trusted certificate authorities.
A censor that controls a certificate authority trusted by the browser
would be able to do a man-in-the-middle attack
between the client and the intermediate web service,
and detect fronting by decrypting TLS and checking for specific Host headers.
Such a censor would be able to detect circumvention,
but still not read the client's plaintext because of the
additional encryption and authentication of the tunneled Tor layer.
It seems risky for the censor to risk being detected in
a man-in-the-middle attack merely to confirm that a user is circumventing,
but it is not impossible for a sufficiently powerful censor.
The problem doesn't exist when the front domain is one
that happens have its public key ``pinned'' in the headless browser,
for instance when using the Chrome extension and fronting through
\urll{www.google.com}.

@@

The key idea of \meek is domain fronting,
but its HTTP tunneling ability is useful on its own.
Another idea for deployment is to use
thousands of simple HTTP reflectors on cheap web hosting
(in place of domain fronting on a big CDN).
The request-reflecting role of a CDN can
be played by a PHP script, for example,
or a special web server configuration.
Their URLs unprotected by domain fronting,
each reflector would be easily individually blockable,
so there would need to be sufficiently many that
a censor could not block them all.
This deployment model is essentially the same as with
ordinary Tor bridges: have lots of volunteer-operated bridges
and make it hard to enumerate them all.
The advantage that an HTTP transport would have
is that it is easier for a volunteer to upload a PHP file to a web host
than to set up and maintain a Tor bridge.

@@

We have presented domain fronting,
an HTTPS technique that uses different domain names
at different communication layers in
order to hide the remote endpoint of a communication.
We implemented \meek,
a pluggable transport for Tor.
We show that it resists common methods of blocking,
and begin an investigation into its
resistance against more subtle and expensive means of traffic analysis.
We discuss the results of an initial deployment of \meek
in both Tor and Psiphon.
